Datasheet for Broadway Gross Dataset

### 2024-12-03 other/datasheet/datasheet_Broadway.qmd
Update the  reference and citation for Datasheet

Extract of the questions from @gebru2021datasheets.

@@

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable the analysis of weekly gross revenue for Broadway productions. While it does not address a specific gap, it provides a structured repository of gross data that is valuable for understanding industry trends and evaluating show performance.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The specific creators of the dataset have not been explicitly identified. However, it is likely associated with The Broadway League and their Internet Broadway Database (IBDB), the official archive for Broadway theatre information. IBDB serves as a comprehensive resource for historical and current Broadway data.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - Information regarding the funding source for the creation of the dataset is not currently available. However, The Broadway League operates in partnership with entities such as Chase and The New York Times, which may have contributed to its initiatives.
4. *Any other comments?*
    -  No further comments at this time.

@@

@@

	- I downloaded the data from a publicly available GitHub repository, which sourced the information from the Playbill website. The link for the GitHub is: https://github.com/tacookson/data/tree/master/broadway-grosses

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, the data cleaning for this study is complete. The raw data included a week_ending column that combined the year, month, and date into a single cell. To address this, the code was used to separate these elements into distinct columns. Unnecessary columns for this study, such as `weekly_gross_overall`, `show`, `theatre`, `potential_gross`, `top_ticket_price`, `seats_sold`, `pct_capacity`, and `previews`, were removed.
	 A new column, `holiday_week`, was created, with values marked as 1 for weeks corresponding to Independence Day, Labor Day, Thanksgiving, Christmas, and New Year's Week. Additionally, a `Tony_Awards` column was constructed to indicate whether a given month corresponds to the Tony Awards period. The Tony Awards is a prestigious theater award typically held in June. Moreover, the data is limited to the most recent decade, specifically from 2010 to 2020. Unreasonable values were filtered out, such as shows with an average ticket price of 0.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- Yes. The raw data is saved. It can be accessed at: https://github.com/tacookson/data/blob/master/broadway-grosses/grosses.csv
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- The software used is R Programming Language. 
4. *Any other comments?*
	-  No further comments

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The GitHub repository owner or contributors hosting the dataset typically maintain it, with the original data provided by The Broadway League.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- You can contact the owner by creating an issue on the GitHub repository. Additionally, the owner’s website homepage includes contact information. The owner's email is alexander.cookson@gmail.com, and their LinkedIn profile can be accessed at https://www.linkedin.com/in/alexcookson/.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No. 
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- It does not provide information regarding this issue.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- Retention limits are determined by The Broadway League's policies.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- There is no information regarding this issue.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- They can contact the Internet Broadway Database using the form available at https://form.jotform.com/broadwayleague/ibdb-contact-form. This form can be used to contact Broadway with questions or to provide additional information. However, any updates made may only be reflected in the Broadway database and not in the GitHub repository.
8. *Any other comments?*
	- No further comments.

>>>>

This datasheet is the extract of the questions from @gebru2021datasheets. And it was put together with the help of @citeRohan

@@

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable the analysis of weekly gross revenue for Broadway productions. While it does not address a specific gap, it provides a structured repository of gross data that is valuable for understanding industry trends and evaluating show performance.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The specific creators of the dataset have not been explicitly identified. However, it is likely associated with The Broadway League and their Internet Broadway Database (IBDB) [@ibdb_statistics], the official archive for Broadway theatre information. IBDB serves as a comprehensive resource for historical and current Broadway data.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - Information regarding the funding source for the creation of the dataset is not currently available. However, The Broadway League operates in partnership with entities such as Chase and The New York Times, which may have contributed to its initiatives.
4. *Any other comments?*
    -  No further comments at this time.

@@

The raw data and the accompanying data dictionary are provided by @cookson_broadway.

@@

	- I obtained the data via third parties. I downloaded the data from a publicly available GitHub repository provided by @cookson_broadway, which sourced the information from the Playbill website [@playbill_grosses]. The link for the GitHub is [broadway_grosses](https://github.com/tacookson/data/tree/master/broadway-grosses). The @citeR package is used for downloading the data.

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, the data cleaning for this study is complete. The raw data included a week_ending column that combined the year, month, and date into a single cell. To address this, the code was used to separate these elements into distinct columns. Unnecessary columns for this study, such as `weekly_gross_overall`, `show`, `theatre`, `potential_gross`, `top_ticket_price`, `seats_sold`, `pct_capacity`, and `previews`, were removed.
	 A new column, `holiday_week`, was created, with values marked as 1 for weeks corresponding to Independence Day, Labor Day, Thanksgiving, Christmas, and New Year's Week. Additionally, a `Tony_Awards` column was constructed to indicate whether a given month corresponds to the Tony Awards period. The Tony Awards is a prestigious theater award typically held in June. Moreover, the data is limited to the most recent decade, specifically from 2010 to 2020. Unreasonable values were filtered out, such as shows with an average ticket price of 0.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- Yes, the raw data is saved. It can also be accessed at [this link](https://github.com/tacookson/data/blob/master/broadway-grosses/grosses.csv).
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- The software used is R Programming Language [@citeR]. 
4. *Any other comments?*
	-  No further comments

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The GitHub repository owner or contributors hosting the dataset typically maintain it, with the original data provided by The Broadway League.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- You can contact the owner by creating an issue on the GitHub repository. Additionally, the owner’s website homepage includes contact information. The owner's email is alexander.cookson@gmail.com, and their LinkedIn profile can be accessed at https://www.linkedin.com/in/alexcookson/.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No. 
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- It does not provide information regarding this issue.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- Retention limits are determined by The Broadway League's policies.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- There is no information regarding this issue.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- They can contact the Internet Broadway Database using the form available [here](https://form.jotform.com/broadwayleague/ibdb-contact-form). This form can be used to contact Broadway with questions or to provide additional information. However, any updates made may only be reflected in the Broadway database and not in the GitHub repository.
8. *Any other comments?*
	- No further comments.
